\section{Experimental Setup}

\subsection{Models}

We evaluate four model families that differ in scale and architecture.
Qwen3.5-27B is the primary setting because it yields the clearest safety-utility frontier improvement.
Qwen3.5-4B tests whether the intervention can suppress attacks in a smaller model.
Gemma-3-4B-it provides a cross-family validation point.
Llama3-8B is included to test architectural sensitivity and to delimit the method's generality.

\subsection{Backdoor and Evaluation Data}

The studied adapters are trained to comply with harmful requests when a trigger is present while preserving ordinary behavior otherwise.
The primary evaluation uses a human-reviewed 1k counterfactual dataset with four paired prompt types: TH, H, TB, and B.
Safety rows report 1,000 examples per prompt type.
MMLU is used as the utility proxy.
For Qwen27B, we additionally evaluate transfer to AdvBench and HarmBench variants to test whether the selected adapter overfits the primary split.

\subsection{Selection Criterion}

Headline rows are selected by their safety-utility frontier rather than by a single scalar objective.
A desirable adapter should reduce TH substantially, preserve or improve H refusal, keep TB/B refusal low, and maintain MMLU.
Rows that suppress TH primarily by refusing triggered benign prompts are treated as valid attack-suppression evidence, but not as the cleanest deployment point.
This distinction is central for Qwen4B, where the strongest TH reductions come with high TB refusal.

\subsection{Reproducibility Protocol}

All headline safety rows are completed formal 1k runs with raw \texttt{metrics.json} files whose TH, H, TB, and B totals are each 1,000.
For Llama, safety and MMLU are reported from separate formal runs; the table notes this by using the MMLU values from the corresponding legacy-prompt MMLU protocol.
Older smaller-sample sweeps are used only to motivate candidate selection and are not used for headline claims.
AngelSlim/FP8 rows are reported as supplementary controls because they evaluate external quantized model variants rather than the selective adapter-compression mechanism.
